---
name: InputFirst
surname: InputLast
position: "Input Titles or Abbreviations"
address: "Input Address"
phone: +1998 765 4321
profilepic: ProfilePic.jpg
email: "youremail@address.edu"
twitter: UsernameOnly
linkedin: FriendlyURL
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Input a short bio here. Describe yourself in a couple of sentences."
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

```{r}
#Beware of Latex and the latex packages needed for compiling. See https://yihui.org/tinytex/r/#debugging if you get any errors related to *.tex compiling 
```

# Education

```{r}
library(rorcid)
library(dplyr)
my_ed <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0001-6229-7514")$`0000-0001-6229-7514`$`affiliation-group`$summaries
)
my_ed %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
# library(tibble)
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
#   "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
#   "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
# ) %>% 
#   detailed_entries(Degree, Year, Institution, Where)
```

# Work experience

```{r}
my_exp <- do.call("bind_rows",
  rorcid::orcid_employments("0000-0001-6229-7514")$`0000-0001-6229-7514`$`affiliation-group`$summaries
)

#For the my_exp variable below: if there is no end date on your recent employment, replace `employment-summary.end-date.year.value` with `employment-summary.end-date`. 
my_exp %>%
  detailed_entries(
    what = `employment-summary.role-title`,
    when = glue::glue("{`employment-summary.start-date.year.value`} - {`employment-summary.end-date.year.value`}"),
    with = `employment-summary.organization.name`,
    where = glue::glue("{`employment-summary.organization.address.city`}, {`employment-summary.organization.address.region`}")
  )

#tribble(
#  ~ Experience, ~ Year, ~ Institution, ~ Details,
#  "Current Job Title", "Years of Employment", "Organization", #"Job Description",
#  "Previous Job Title", "Years of Employment", "Organization", #"Job Description",
  
#) %>% 
#  detailed_entries(Details, Year, Experience, Institution)
```
# Languages:
  
  * **English**: native language.
  * **Spanish**: advanced speaking, writing and reading.
  * **French**: intermediate speaking, writing and reading.

# Skills
These are some of the skills and knowledge I aquired during my training, education and courses

  * **First overarching skillname**:  
      List the details, including software, techniques, etc.
  * **Second overarching skillname**:  
      List the details, including software, techniques, etc.
  * **Other informatic tools**:  
      Microsoft Office; Google Suite; GraphPad Prism; LaTeX; Git; HTML & CSS.
  * **Public speaking**:  
      I  have attended and presented my scientific work in several national and international conferences, both orally and in poster format.
      
# Publications

```{r}
library(rorcid)
library(tidyverse)
out <- works(orcid_id("0000-0001-6229-7514")) 
 tibble(
   Journal = out$`journal-title.value`,
   Title = out$title.title.value,
   Year = out$`publication-date.year.value`,
   DOI = out$url.value
 ) %>% 
  detailed_entries(
  DOI,
  Journal,
  Title,
  Year
)

```

